Weak interspecific interactions in a sagebrush steppe: evidence from observations, models, and experiments

### 2017-09-11 removals/manuscript/ResponseToReviews.tex

\begin{document} 
\centerline{\large{Response to reviews}}

\normalsize

Dear Tom,

We really appreciated the quality of the reviews we received. Both reviewers and yourself clearly ``got" the paper -- both its strengths and weaknesses. We have revised the ms. to highlight those strengths and shore up the weaknesses. In particular, we have 1) added text to the Introduction and Discussion to emphasize the importance, generality, and novelty of our work, and 2) added new text and supplementary figures to the Methods to justify the decisions we made in designing our data analysis. In our point-by-point response below, the original reviewer comments are in black and \response{our responses are in blue.} We hope you fill this version of the manuscript suitable for publication.

@@

My own main concern overlaps with Reviewer 1 regarding the clarity and interpretation of your statistical analysis. The manuscript sends mixed messages about how you estimated the removal treatment coefficient. There are (at least) two ways to do this. You could (A) fit a full model, including a removal coefficient (Eq 1), to all the data and evaluate significance of the removal term. This is suggested by the sentences at lines 171-173 ('note that these are not estimated as separate models'). Or you could (B) fit the crowding coefficients (your $\omega_{jm}$) from the control plots, then use them (as fixed values) in a second round of models fit to the removal plots that include a removal term (as a free parameter) and evaluate the significance of this coefficient. This is suggested at lines 263-268 ('would indicate effect larger or smaller than predicted by a model based on data from control plots'). Reviewer 1 and I have the intuition that method B is a better way to evaluate whether observational data can predict the effects of removals. Under method A (if that is what you did), I do not see why the treatment coefficient would be interpreted as the under- or over-estimation of competition. If the full model is fit to all the data, then the removal coefficient should instead reflect the difference between control and removal plots that is not related to competition, especially if both plot types spanned similar ranges of crowding environments, as you suggest (lines 289-293). This could perhaps be some unintended effect of herbicide or spatial location. In your revision, please take care to improve the communication and justification of your methods for testing whether observational data can predict the effects of experimental removals.

\response{ This is an insightful comment, and we understand your point. There are two reasons why your suggested approaches A and B will not differ in our case. First, to answer Reviewer 1's question about this same issue, ``including the removal experiment data in model fitting \emph{does not} alter the estimates of (intra- and inter-specific) competition parameters," or any other parameters for that matter. We estimated a version of our P. spicata growth model using only data from control plots. The correlation between the parameters estimated by that model and the parameters estimated by a model fit to all data is 0.99983. Results for P. secunda were similar.  So there is no evidence of interactions between the removal treatment and other parameters in the model. Second, to clarify why all the differences between demographic performance in control and removal plots can be captured by one removal coefficient that only alters the overall intercept, we drew a new figure (Appendix C-2). To generate this figure, we fit a version of the growth model for P. spicata that did not include crowding from A. tripartita, but includes all other terms in our full model. We then plotted the residuals from this model against the observed values of A. tripartita crowding, using different colors from points for the control plots and the A. tripartita removal plots. The control plots points stretch out across the x-axis from A. tripartita values of zero up to a maximum of 70, and demonstrate a very weak but negative relationship between A. tripartita crowding and P. spicata growth. The slope of this line is the competition coefficient we estimate. However, all of the points for the removal plots, where A. tripartita cover is zero by design, are stacked on top of each other at x = 0. The figure shows that P. spicata plants experiencing zero A. tripartita crowding are growing faster in removal plots than in control plots, but it also shows why our removals provide no inference about the slope of the fitted line. So you are correct that we cannot clearly distinguish between two potential causes of the positive removal effect, one being that our observational data lead to an underestimate of A. tripartita competitive effects, and the other being that, in your words, ``the difference between control and removal plots...is not related to competition."  In retrospect, rather than only doing complete A. tripartita removals, we should have included partial removals. That said, while we now know how to conduct an even stronger test of our model in the future, the test we did conduct does represent a significant advance beyond the existing state of the art. To clarify these issues, we have added a new paragraph to the Methods section, along with the new Appendix figure (C-2). We also mention in the Discussion how we would do it differently next time.}

@@

Other suggestions:

- The abstract can be strengthened all around. It is very narrowly motivated (first words: 'A previous study').

\response{We revised the abstract to broaden the motivation.}

@@

- Figure 5: You incorporate random year effects into these cover estimates, so they are basically the stationary distributions of cover. Your vital rate models included spatial random effects. Can you incorporate these too?

\response{We could. In fact, for our short-term population projections, which we compare directly to observed cover values, we do include spatial random effects. However, for these long-term projections, we just wanted to focus on changes in cover for a hypothetical, average plot. If we incorporated the spatial random effects, we would six slightly different versions of this plot, but because none of the other parameters vary spatially, the effects of removals on each species would not change much at all. We have added a sentence to the Methods justifying our choice to exclude spatial variation. }

- You find that competitive interactions are weak, and that your models do a good job at predicting them. I could imagine that weak interactions make removal effects easy to predict (nothing happens!). You conclude that the success of this case study supports the use of multi-species models built from observational data. Do you think this conclusion will apply to communities with stronger competition? You might address this issue in your Discussion.

\response{We added a new "lessons learned" paragraph to the Discussion where we address this point (yes, we see no reason why
multispecies models would not also work in communities with stronger competition), along with other generalizations 
from our experience on this project.  }

@@

\response{Thank you for the positive feedback!}

Major comments:

Originally I did not realize that you were fitting one model to the survey and removal experiment simultaneously. I thought that you would want to separate the data used to parameterize the model vs. the data used to test the model.  I wonder how much the removal experiment data is influencing parameters (other than the removal effect) in the model. One constraint of using survey data to fit models is that often natural communities do not experience a wide range of conditions (i.e., grass and Artemisia both at low cover or a rainy year with low crowding). Does including the removal experiment data in model fitting alter the estimates of (intra- and inter-specific) competition parameters because it encompasses combinations of the dependent variables that do not exist in the survey? This may particularly be important for the grass removal plots because they did not go to 0 immediately and thus exhibit variability (such that the model might want to adjust the slope/competition parameter rather than add a removal intercept effect). I think you tried to address this issue with Figure C-3 but I was confused by that graph (see minor comments below), and I think it would be better to either to 1) mathematically argue that the experimental data does not influence parameters other than the removal effect or 2) fit models using only the survey data and show that the parameter estimates are unchanged.

\response{We addressed this point above, in response to Miller's comments. Briefly, adding data from the removal experiments does not alter estimates of competition coefficients, but rather alters estimated of model intercepts because crowding from removed species must equal zero. As a result, a separate intercept for removal plots captures the effects of the removals. We have clarified this in a new Methods paragraph and an additional Appendix figure (C-2).}

@@

Possibly related to this – where the removal and competition parameters correlated?

\response{We are not sure what correlation the reviewer is interested in (correlations in the MCMC chains?), but perhaps our assurance that
adding the removal data does not alter the competition coefficients helps allay the implicit concern.}

@@

Another thing that kept crossing my mind as I read the paper was about the treatment of “non-significant” parameters, i.e., parameters with high uncertainty. As far as I could tell throughout the paper, parameters were never dropped from models, and projections were done using the parameter estimates based on the mean of the MCMC chain values. I was struggling with what it means to use parameters with high uncertainty in projections. You explain that you want to use the deterministic versions of the models (line 186) rather than a draw from the Poisson random variable; however those deterministic values of lambda have uncertainty. In your simulations you could incorporate that uncertainty by taking a random draw from the MCMC chain for each parameter (I don't know if this is standard practice). It seemed that this would somehow “equalize” parameter uncertainty (in competition, yearly intercept, removal parameters, etc.). I’m not sure if this would change the conclusions, the only thing it might do is make the variance larger in Fig. 5, and thus the P. spicata Removal model/no ARTR might not look as different from the other P. spicata models. I’m not saying you need to do this, I’m just curious if you had considered this issue at all.

\response{ This is a good point, and we appreciate being pushed to justify our decision to ignore parameter uncertainty. Our goal is to test
whether competitive release is as small as our previous model predicted. To be conservative, we want to make it as easy as possible to
model large effects of removals. (That is why we included the ``maximum removal effect" simulation based on the outer limits of the removal effect
confidence intervals.) Propagating parameter uncertainty through our simulations would add noise, making it \emph{harder} to 
detect the effects of removals. More formally, our previous result showed that the interspecific competition coefficients are small in an ecologically
relevant sense: the shift in mean cover due to interspecific competition shown in Fig. 5 is (for 3 species) small compared to the natural fluctuations in cover driven by interannual environmental variability. 
If, as suggested, we made the projections with parameter uncertainty on top of random year effects, we would be conflating parameter uncertainty with environmental variability, ``tilting'' the
comparison in our favor by overstating the magnitude of natural fluctuations. One point of Fig. 5 is that for \emph{P. spicata} the small effect of competition with ARTR each year adds up (in the model) to a nontrivial long-term effect. We have added a new paragraph to the Methods section "Individual Based Models" that makes these points. }

@@

My last comment, and really the only negative thing I can say about this paper is that it comes across as rather confirmatory in nature. It is absolutely solid science and 
highly interesting and important but the writing does not punch you with novelty. I think some small changes in wording could highlight that this is quite novel and hasn't 
been assessed in any other systems.

\response{We all agreed that this is the first time we have been accused of underselling a result! We have added a new paragraph to the Introduction
to highlight the novelty of our approach and to show how it answers a growing chorus of calls for more predictive tests. Also, in the Discussion, we 
added some text to further emphasize why our study is a strong test of a prediction. }

@@

Lines 137-139:  When did you survey the removal plots? What month and for how many years?

\response{We added the following sentence, "We repeated mapped censuses of all plots each June from 2012-2016."}

Lines 150-173: In this section, I was confused what plots (survey plots or removal experiment) you were using to fit the models. Originally I had thought you would use only the survey plots to fit the models, then hold those parameters constant and add the removal parameter and fit the models to the removal data. I had thought that you would want to separate the data used to parameterize the model vs. the data used to test the model. I then realized that you were fitting the model to all data simultaneously (survey and removal experiment). Maybe be explicit somewhere?

\response{The new Methods paragraph addresses these questions directly.}

@@

\response{Yes, we now clarify this in the new Methods paragraph on parameter uncertainty. Note that most of the parameters close
to zero are the interspecific interaction effects. If we set those to zero, or dropped them from the simulations, it would further reduce the 
magnitude of competitive release predicted by the model.}

Results

Line 263:  When I read this I wanted to know something about the uncertainty in these parameters – do most credible intervals overlap zero, or are the coefficients small but “significant”?

\response{We added this sentence: ``The intraspecific interaction effects are large and have credible intervals that do not overlap zero, while the interspecific coefficients are small and the majority have credible intervals that do overlap zero." }

@@

Lines 277-283: Does the root zone of Artemisia generally fall under its canopy? Or is it larger in diameter than the aboveground canopy? Do you think the primary limiting resource is nutrients/moisture or light?

\response{We altered this section to be clear that competition for light or for soil resources should be stronger under the canopy. We also added a caveat in the Discussion (in response to Reviewer 2) about roots extending beyond canopies. }

Line 291: Can you add some explanation to the “break covariances in plant densities” part? It took me a while to figure out what you meant.

\response{We replaced ``break covariances in plant densities among species" with ``result in combinations of neighborhood-scale densities that deviate from naturally occurring patterns of correlation."}

@@

Fig. 1: I’m confused how the focal species account for 70\% basal and 60\% canopy cover (as stated in the methods), but the mean cover values for the grasses in Fig. 1 range from only 1-3\%. I realize your estimates of cover were highly precise, but it seems that it would be hard to model species that are at such low abundance.

\response{We addressed this point in detail in response to Reviewer 2's comment below.}

Fig. 4. I imagine you omitted error bars from these graphs b/c it might get messy, but I would like to see them (possibly in the supplement). It would be helpful, especially for P. spicata, to assess how off the predictions were, i.e. do error bars overlap?

\response{The requested figure is included below (Fig. 1). It shows broad overlap, but we think it is too messy to include in the supplement. }

 \begin{figure}[tbp]
 \centering
 \includegraphics[width=1\textwidth]{cover_projections_1stepBARS}
 \caption{ Same as Fig. 4 in the main text, but with error bars showing 1 standard deviation of the mean. }
 \label{fig:projectionsBars}
 \end{figure}

@@

\response{We revised the legend to clarify that the red points for Artemisia are pre-treatment values.}

Reviewer: 2

This study investigates whether models parameterized from historical data sets accurately describes
interspecific interactions by assessing whether additional terms are needed to account for removal
results beyond predictions from non-experimental data sets. Previous work led by Adler using models
based on historical data has produced important results, e.g., on the role of the storage effect and of
niche vs neutral processes in community dynamics, so I applaud their attempt to confirm model validity
and strengthen those results. On the other hand, I do have some concerns about the robustness of the
results, as described below. More broadly, even if the conclusions are robust, the manuscript could use
greater efforts to generalize beyond the validity of these particular models for these species. It would
be much appropriate for a general journal such as Ecology if the results were used to draw conclusions
on when modeling approaches will underestimate or overestimate interaction effects. Focusing the
discussion on such questions would be more appropriate than the current discussion material on
coexistence and inter- vs intraspecific competition, which are not part of the research questions that
end the Introduction.

\response{We have added new Discussion paragraph to directly address these questions about methodological
generalizations (lines ???). }

@@

One concern in the design is based on the relatively low covers, especially of the grasses. Based on
Figure 1, basal grass cover per species is very low even before removal—1-2\% per species. Finding
significant effects of such low cover on shrubs would indeed be surprising. Given this low expectation,
this does not seem a very strong test of whether model predictions are valid or not for the shrub. Does
the model even predict any effect of grass removals at these levels? Should the grass removal
treatment even be included in the study? The parameters estimated for A. tripartita seem to be very
uncertain in any case (pp 16-17), further suggesting that the results for this species do not add the story.

\response{We can offer multiple lines of evidence that low grass cover is not the cause of weak grass effects. 
First, grass cover is high enough to cause strong intraspecific competition. The puzzle is why interspecific effects
of grasses are so weak when their intraspecific effects are strong. Second, our growth and survival models do not
depend on average cover but rather neighborhoood scale cover: even if average cover is low, a
grass species may reach high abundance in a particular neighborhood, as seen in the Appendix figures
showing distribution of crowding values, and exert strong per-unit-area effects on another plant. The grasses do in fact
affect Artemisa, as shown in Tables B-2 (marginally significant effect of H. comata on Artemisia survival), B-6 (significant 
effect of Poa on Artemisia growth, and  B-15 (P. spicata has a positive effect on Artemisia recruitment, while H. comata
has a negative effect; the 95\% CIs do not overlap zero). Finally,
grasses are mapped in the currency of basal cover, while for Artemisia canopy cover is mapped. To help readers
appreciate that small values of basal cover are not trivial, we have added a new supplementary figure (C-1) showing 
photos of example quadrats before and after the removal treatment.  }

### 2017-09-11 removals/manuscript/removal_ms.tex
Done with revisions for now.

A previous study of four dominant species in a sagebrush steppe community used historical data sets and multispecies population models to demonstrate weak interspecific interactions and predicted that little competitive release would result from removal of heterospecific competitors. We conducted a removal experiment to test whether our model, with weak interspecific competition, accurately describes interspecific interactions. Our removal treatments were 1) removal of all perennial grasses and 2) removal of the dominant shrub, \textit{Artemisia tripartita}. We \new{regressed} survival, growth and recruitment on the locations, sizes, and species identities of neighboring plants, along with an indicator variable for removal treatment. If our ``baseline" \new{regression} model, which accounts for local plant-plant interactions, accurately explains the observed responses to removals, then the fitted removal indicator effect should be non-significant. For survival and recruitment, the removal treatment effects were never significantly positive, indicating that the baseline model did not underestimate intraspecific competitive effects. For \textit{Poa secunda} recruitment, the removal treatment was negative, indicating that our baseline model overestimated intraspecific competition. For growth, the removal treatment effect was significant and positive for two species, \textit{Poa secunda} and \textit{Pseudoroegneria spicata}, indicating that the baseline model underestimated intraspecific competitive effects. However, including information about the location of grass individuals with respect to removed \textit{A. tripartita} failed to improve the growth regressions, raising questions about the mechanisms driving the positive response to removal. For three species, population projections based on the vital rate regressions showed little impact of removals on population growth rates or equilibrium cover. For \textit{P. spicata}, the population models that included effects of \textit{A. tripartita} removal projected greater competitive release than the baseline models. The ability of models based on observational data to predict population responses to experimental removals increased our confidence that interspecific interactions are in fact weak for at least three of our four study species. The implication is that factors besides interspecific \new{feedbacks} play important roles in determining the structure and dynamics of this community. The success of the models also supports the use of multispecies models based on long-term observational data for  characterizing competitive interactions.

@@

In spring 2011, in a large exclosure containing six of the historical permanent quadrats, we established an additional 16 quadrats for the removal treatments. New quadrats were selected to be similar to historical plots, but also needed to have enough of the focal species present so that removal experiments could be conducted. We evaluated potential locations for the new quadrats near the original quadrats and then used only those locations with at least 5\% canopy cover of \textit{Artemisia tripartita} and at least 3\% combined basal cover of the three focal perennial grasses. We rejected locations falling on hill slopes, areas with greater than 20\% bare rock, or with over 10\% cover of the woody shrubs \textit{Purshia tridentata} or \textit{Amelanchier utahensis}. We mapped the new quadrats in June, 2011 and then implemented the removal treatments in September, 2011. We randomly assigned 8 of the sixteen new quadrats to the sagebrush removal treatment, and the remaining 8 to the grass removal treatment. We cut sagebrush stems at ground level and applied a 5\% solution of Roundup Pro (Glyphosate, Monsanto) to the cut stems. In the grass removal plots, we painted the same herbicide solution on all perennial grasses. We removed plants 50 cm beyond the quadrat boundaries to minimize edge effects. The sagebrush removal was virtually 100\% effective; grass removals required additional herbicide applications in April and May of each year, with fewer grasses remaining each year. We repeated mapped censuses of all plots each June from 2012-2016.

@@

If the conspecific and heterospecific crowding effects, the $\omega_{jm}$'s, explain demographic rates in removal treatment plots as well as they do in control plots, then there will be no need for the removal treatment effect, and the estimated coefficient will be small and not significantly different from zero. However, if demographic rates in removal plots differ from control plots even after accounting for crowding effects, then the removal treatment effect will be significant. For example, we might find that, holding crowding constant, grasses grow more quickly in the sagebrush removal plots than in the control plots. This result would indicate that predictions from a ``baseline model'', a model including all estimated parameters except for the removal treatment effect, underestimates competitive release. We refer to the model that includes the estimated removal treatment effect as the ``removal model". Note that these are not estimated as separate models; we estimate all parameters together, but when we generate predictions from the baseline model, we simply set the removal treatment effects to zero.

@@

We simulated the IPM to estimate equilibrium abundances under three different scenarios. \new{In all of these simulations, we set the spatial random effects to zero, meaning that we are simulating dynamics on a hypothetical, average site.} To incorporate temporal environmental variation, at each time step we randomly selected one of the 30 sets of random year effects for the survival, growth and recruitment models (``kernel selection'' in the terminology of \citealt{metcalf_statistical_2015}). For each scenario, we initialized all species with very low cover and ran the model for 500 time steps (years) to allow the community to reach its equilibrium (i.e., its steady-state pattern of fluctuations in response to environmental variability). We calculated the \new{average steady-state cover} for each species by simulating an additional 2000 time steps and averaging each species' cover over this period.} The first scenario featured all four species and our baseline model for control plots (no removal effects). For the second scenario, we simulated our experimental removals by setting either the cover of \textit{A. tripartita} to zero or the cover of all three grass species to zero, and then simulating the dynamics of the remaining species as under the first scenario. This simulation projects competitive release following removal according to the baseline model (no removal effects). For the third scenario, we again set \textit{A. triparitia} or grass cover to zero, but this time we projected the model using the vital rate regressions that include removal effects. If our baseline model successfully predicts competitive release observed in the removal experiment, then the results of the second and third scenarios should be similar. To the extent that the baseline model underestimates (or overestimates) the actual competitive release, the results of the second and third scenarios will differ. As with the IBM, we repeated these simulations using maximum removal treatment effects represented by parameters values at the 5\% or 95\% credible limit farthest from zero.

@@

Our population models based on historical, observational data reveal weak interspecific interactions \citep{adler_coexistence_2010,chu_large_2015}. As a result, the 
models predict very little competitive release among the four dominant species in a sagebrush steppe. Because the models were based solely on observational
data, we were suspicious of our model's ability to accurately describe interspecific interactions, so we conducted a removal experiment to test it. 
The results provide substantial support for our model's predictions, and for the weakness of interspecific interactions in this community.

% not sure yet where this should go
\new{Our study represents a very strong test of a surprising prediction for two reasons. First, the prediction was already published; the experiment 
represented a very real chance of getting it wrong...Second, we were just testing an observationally based model with new observations, but rather with
an experimental manipulation, increasing the potential to confront the model with a novel situation outside the historical range of variation... Add Steve's point about testing population models--in contrast to the Crone study, we do well when we control for environmental variation with random year effects...}

@@

The weak interspecific interactions among many of the dominant species in our system implies that these species  
are limited by quite different factors. This low niche overlap could reflect strong resource partitioning \citep{tilman_resource_1982}, 
perhaps combined with variation in the times and locations at which species are taking up those resources. 
Species-specific responses to spatial and temporal variation in non-resource environmental variables can also weaken interspecific 
interactions \citep{chesson_mechanisms_2000}, though in a previous study we failed to find evidence of a temporal storage effect 
in this community \citep{adler_weak_2009}. Interactions with above- or belowground enemies can regulate populations and, given 
enough species-specificity in the effects of these enemies, decouple the dynamics of different species \citep{hersh_evaluating_2011,
janzen_herbivores_1970,connell_role_1971}.  More likely, plants may alter the environment, and even resource availability, 
in ways that facilitate their neighbors. For example, shade cast by \textit{A. tripartita} canopies may reduce 
evapotranspiration (e.g. \citealt{Barbier2008}). \textit{A. tripartita} removal might offset this facilitative effect by reducing 
resource uptake, resulting in little net change in water balance following removal. 
Unfortunately, we did not monitor soil moisture at the fine spatial and temporal resolution necessary to test this hypothesis.

@@

\section*{Acknowledgements}
Funding was provided by NSF grants DEB-1353078,and  DEB-1054040 to PBA and DEB-1353039 to SPE and GH, and by the Utah Agricultural Experiment Station. 
The USDA-ARS Sheep Experiment Station generously provided access to historical data and the field experiment site. 
We thank Robin Snyder for suggestions that improved the manuscript.

@@

@@

  \begin{figure}[tbp]
  \centering
  \includegraphics[width=1\textwidth]{PSSP_W_scatters}
  \caption{Bivariate scatter plots comparing crowding exerted by each neighbor species on \textit{P. spicata}. \response{Each point compares the crowding experienced by one \textit{P. spicata} individual in one year from the species on the x-axis to the species on the y-axis.}   Blue symbols show values from controls plots, red symbols show \new{pre-treatment} values from \textit{Artemisia} removal plots.``W.allcov'' refers to the aggregated crowding by all shrubs and perennial grasses beyond the focal dominant species, and ``W.allpts'' refers to the aggregated crowding by forb species.  \texttt{Wdistrib\textbackslash exploreSurvivalWs.r}. }
  \label{fig:Wscatters}
  \end{figure}

@@

 \begin{figure}[tbp]
 \centering
 \includegraphics[width=1\textwidth]{cover_projections_1step_maxCI}
 \caption{Observed and predicted cover for each of the four modeled species assuming maximum effects of removal. 
  Solid black lines show mean observed cover averaged across control (closed symbols) and removal treatment (open symbols) quadrats. Blue lines and symbols show one-step-ahead predictions from the baseline IBM (no removal treatment coefficients), averaged across quadrats. Red lines and symbols show one-step-ahead predictions from an IBM that includes removal treatment coefficients. 
  Source file: \texttt{ibm\textbackslash summarize\textunderscore sims1step.r}. }
 \label{fig:IBM1step-maxCI}
 \end{figure}

>>>>

\new{Stable coexistence requires intraspecific limitations to be stronger than interspecific limitations. The greater the difference between intra- and interspecific limitations, the more stable the coexistence, and the weaker the competitive release any species should experience following removal of competitors. We conducted a removal experiment to test whether a previously estimated model, showing surprisingly weak interspecific competition for four dominant species in a sagebrush steppe, accurately predicts competitive release.} Our removal treatments were 1) removal of all perennial grasses and 2) removal of the dominant shrub, \textit{Artemisia tripartita}. We \new{regressed} survival, growth and recruitment on the locations, sizes, and species identities of neighboring plants, along with an indicator variable for removal treatment. If our ``baseline" \new{regression} model, which accounts for local plant-plant interactions, accurately explains the observed responses to removals, then the removal coefficient should be non-significant. For survival and recruitment, the removal coefficients were never significantly positive, indicating that the baseline model did not underestimate intraspecific competition. For \textit{Poa secunda} recruitment, the removal coefficient was negative, indicating that our baseline model overestimated intraspecific competition. For growth, the removal treatment effect was significant and positive for two species, \textit{Poa secunda} and \textit{Pseudoroegneria spicata}, indicating that the baseline model underestimated intraspecific competition. However, including information about the location of grass individuals with respect to removed \textit{A. tripartita} failed to improve the growth regressions, raising questions about the mechanisms driving the positive response to removal. For three species, population projections based on the vital rate regressions showed little impact of removals. For \textit{P. spicata}, the population models that included effects of \textit{A. tripartita} removal projected greater competitive release than the baseline models. The ability of models based on observational data to predict population responses to experimental removals increased our confidence that interspecific interactions are in fact weak for at least three of our four study species. The implication is that factors besides interspecific \new{feedbacks} play important roles in determining the structure and dynamics of this community. The success of the models also supports the use of multispecies models based on long-term observational data for characterizing competitive interactions.

@@

In spring 2011, in a large exclosure containing six of the historical permanent quadrats, we established an additional 16 quadrats for the removal treatments. New quadrats were selected to be similar to historical plots, but also needed to have enough of the focal species present so that removal experiments could be conducted. We evaluated potential locations for the new quadrats near the original quadrats and then used only those locations with at least 5\% canopy cover of \textit{Artemisia tripartita} and at least 3\% combined basal cover of the three focal perennial grasses. We rejected locations falling on hill slopes, areas with greater than 20\% bare rock, or with over 10\% cover of the woody shrubs \textit{Purshia tridentata} or \textit{Amelanchier utahensis}. We mapped the new quadrats in June, 2011 and then implemented the removal treatments in September, 2011. We randomly assigned 8 of the sixteen new quadrats to the sagebrush removal treatment, and the remaining 8 to the grass removal treatment. We cut sagebrush stems at ground level and applied a 5\% solution of Roundup Pro (Glyphosate, Monsanto) to the cut stems. In the grass removal plots, we painted the same herbicide solution on all perennial grasses. We removed plants 50 cm beyond the quadrat boundaries to minimize edge effects. The sagebrush removal was virtually 100\% effective; grass removals required additional herbicide applications in April and May of each year, with fewer grasses remaining each year. Appendix Fig. \ref{fig:photos} shows photographs of example quadrats before and after treatment. We repeated mapped censuses of all plots each June from 2012-2016.

@@

If the conspecific and heterospecific crowding effects, the $\omega_{jm}$'s, explain demographic rates in removal treatment plots as well as they do in control plots, then there will be no need for the removal treatment effect, and the estimated coefficient will be small and not significantly different from zero. However, if demographic rates in removal plots differ from control plots even after accounting for crowding effects, then the removal treatment effect will be significant. For example, we might find that, holding crowding constant, grasses grow more quickly in the sagebrush removal plots than in the control plots. This result would indicate that predictions from a ``baseline model'', a model including all estimated parameters except for the removal treatment effect, underestimates competitive release. We refer to the model that includes the estimated removal treatment effect as the ``removal model".

\new{Note that the ``baseline" and ``removal" models are not estimated separately; we estimate all parameters together, but when we generate predictions from the baseline model, we simply set the removal treatment effects to zero. We chose this over an alternative approach of fitting a model only to data from control plots and then making and evaluating predictions for the removal plots. The principal advantage of our approach is that the significance test (confidence intervals) for the removal effect is well-defined; we do not know of valid tests for fitting on one data set and testing on another (GILES??). In addition, the alternative approach would return essentially the same results because adding data from the removal plots had negligible effects on other model parameters. Correlations between the parameters of a model fit only to control plot data and our full model (leaving aside the removal effects) were stronger than 0.999. Why don't we find strong interactions between removal treatments and the estimated competition coefficients? The answer is that because our treatments involved complete, not just partial, removal of target species, their effects can be captured with an intercept term, as illustrated in Fig. \ref{fig:PSSPresids}. As a result, if, for example, one of the grasses responds more positively to removal of \textit{A. tripartita} than our baseline model predicts, we cannot determine whether this reflects a release from competition (i.e. a poorly estimated competition coefficient) or some other effect of our removal treatment  independent of competitor densities.   }

@@

We simulated the IPM to estimate equilibrium abundances under three different scenarios. \new{In all of these simulations, we set the spatial random effects to zero, meaning that we are simulating dynamics on a hypothetical, average site.} To incorporate temporal environmental variation, at each time step we randomly selected one of the 30 sets of random year effects for the survival, growth and recruitment models (``kernel selection'' in the terminology of \citealt{metcalf_statistical_2015}). For each scenario, we initialized all species with very low cover and ran the model for 500 time steps (years) to allow the community to reach its equilibrium (i.e., its steady-state pattern of fluctuations in response to environmental variability). We calculated the \new{average steady-state cover for each species by simulating an additional 2000 time steps and averaging each species' cover over this period.} The first scenario featured all four species and our baseline model for control plots (no removal effects). For the second scenario, we simulated our experimental removals by setting either the cover of \textit{A. tripartita} to zero or the cover of all three grass species to zero, and then simulating the dynamics of the remaining species as under the first scenario. This simulation projects competitive release following removal according to the baseline model (no removal effects). For the third scenario, we again set \textit{A. triparitia} or grass cover to zero, but this time we projected the model using the vital rate regressions that include removal effects. If our baseline model successfully predicts competitive release observed in the removal experiment, then the results of the second and third scenarios should be similar. To the extent that the baseline model underestimates (or overestimates) the actual competitive release, the results of the second and third scenarios will differ. As with the IBM, we repeated these simulations using maximum removal treatment effects represented by parameters values at the 5\% or 95\% credible limit farthest from zero.

@@

\subsection*{An experimental test of model predictions}

Our population model based on historical, observational data revealed weak interspecific interactions \citep{adler_coexistence_2010,chu_large_2015}. As a result, the model predicts very little competitive release among the four dominant species in a sagebrush steppe. 
Because the model was based solely on observational
data, we were suspicious of its ability to accurately describe the outcome of interspecific interactions, so we conducted a removal experiment to test it. 
\new{Our approach represents a strong test of a surprising prediction for two reasons. First, the prediction was already published; the experiment 
gave us a very real opportunity to be publicly wrong. Second, testing an observationally-based model with an experimental manipulation, 
not just additional observations, further increases the potential to confront the model with a novel situation outside the historical range of variation.}
The results provide substantial support for our model's predictions, and for the weakness of interspecific interactions in this community.

@@

\new{What general lessons can we draw about testing predictions from population models? 
First, partial removals, rather than complete removal treatments, could 
have helped us to distinguish between competition-mediated and density-independent effects of removal treatments (e.g. Fig. \ref{fig:PSSPresids}) 
Future work in other systems might benefit from this insight. Second, the success of our models supports the use of long-term observational data for characterizing competitive interactions. We see no reason why this approach would not work just as well in a community with stronger 
interspecific interactions. After all, our approach did detect strong intraspecific effects. 
Finally, our results give cause for optimism about population forecasting.
\citet{Crone2013} found that matrix projection models for plants failed to forecast population trends due environmental differences 
between the data collection and forecast periods. Our population models performed quite well after accounting for year-to-year 
environmental variation with random year effects. }

\subsection*{Implications of weak interspecific interactions}

The weak interspecific interactions among many of the dominant species in our system indicates that these species  
are limited by quite different factors. This low niche overlap could reflect strong resource partitioning \citep{tilman_resource_1982}, 
perhaps combined with variation in the times and locations at which species are taking up those resources. 
Species-specific responses to spatial and temporal variation in non-resource environmental variables can also weaken interspecific 
interactions \citep{chesson_mechanisms_2000}, though in a previous study we failed to find evidence of a temporal storage effect 
in this community \citep{adler_weak_2009}. Interactions with above- or belowground enemies can regulate populations and, given 
enough species-specificity in the effects of these enemies, decouple the dynamics of different species \citep{hersh_evaluating_2011,
janzen_herbivores_1970,connell_role_1971}.  More likely, plants may alter the environment, and even resource availability, 
in ways that facilitate their neighbors. For example, shade cast by \textit{A. tripartita} canopies may reduce 
evapotranspiration (e.g. \citealt{Barbier2008}). \textit{A. tripartita} removal might offset this facilitative effect by reducing 
resource uptake, resulting in little net change in water balance following removal. 
Unfortunately, we did not monitor soil moisture at the fine spatial and temporal resolution necessary to test this hypothesis.

@@

\section*{Acknowledgements}
Funding was provided by NSF grants DEB-1353078 and DEB-1054040 to PBA and DEB-1353039 to SPE and GH, and by the Utah Agricultural Experiment Station, which approves this contribution as journal paper number 9033. 
The USDA-ARS Sheep Experiment Station generously provided access to historical data and the field experiment site. 
We thank Robin Snyder, Tom Miller, and two anonymous reviewers for suggestions that improved the manuscript.

@@

 \begin{figure}[h]
 \centering
 \includegraphics[width=0.7\textwidth]{plate}
 \caption{Examples of a grass removal quadrat before treatment in 2011 (A) and four years after treatment in 2015 (B), and an \textit{A. tripartita} removal quadrat before treatment in 2011 (C) and again in 2015. Basal cover of the perennial grasses in (A) was 4.6\% and canopy cover of  \textit{A. tripartita} in (B) was 22.9\%. }
 \label{fig:photos}
 \end{figure}

 \begin{figure}[h]
 \centering
 \includegraphics[width=0.7\textwidth]{PSSP_marginalWARTR}
 \caption{Marginal effects of \textit{A. tripartita} crowding (W) on \textit{P. spicata} growth. Points are residuals from a model that included all 
 covariates from our standard model except for \textit{A. tripartita} crowding. Grey points show (residual) growth of individual plants in control plots, red points show plants in \textit{A. tripartita} removal plots. The blue symbol shows the mean of the red points. Source file: \texttt{growth\textbackslash PSSPgrowth.r}. }
 \label{fig:PSSPresids}
 \end{figure}

@@

  \begin{figure}[tbp]
  \centering
  \includegraphics[width=1\textwidth]{PSSP_W_scatters}
  \caption{Bivariate scatter plots comparing crowding exerted by each neighbor species on \textit{P. spicata}. \new{Each point compares the crowding experienced by one \textit{P. spicata} individual in one year from the species on the x-axis to the species on the y-axis.}   Blue symbols show values from controls plots, red symbols show \new{pre-treatment} values from \textit{Artemisia} removal plots.``W.allcov'' refers to the aggregated crowding by all shrubs and perennial grasses beyond the focal dominant species, and ``W.allpts'' refers to the aggregated crowding by forb species.  \texttt{Wdistrib\textbackslash exploreSurvivalWs.r}. }
  \label{fig:Wscatters}
  \end{figure}

@@

 \begin{figure}[tbp]
 \centering
 \includegraphics[width=1\textwidth]{cover_projections_1step_maxCI}
 \caption{Observed and predicted cover for each of the four modeled species assuming maximum effects of removal. 
  Solid black lines show mean observed cover averaged across control (closed symbols) and removal treatment (open symbols) quadrats. Blue lines and symbols show one-step-ahead predictions from the baseline IBM (no removal treatment coefficients), averaged across quadrats. Red lines and symbols show one-step-ahead predictions from an IBM that includes removal treatment coefficients assigned the outermost value of the 95\% credible intervals. 
  Source file: \texttt{ibm\textbackslash summarize\textunderscore sims1step.r}. }
 \label{fig:IBM1step-maxCI}
 \end{figure}
